Software Citation Principles

### 2016-03-16 sc-principles/software-citation-principles.tex
adding a paragraph in 5 on software papers

>>>>

\textbf{Software papers}

Currently, and for the foreseeable future, software papers are being published and cited,
in addition to software itself being cited, as many community norms and practices are
oriented towards citation of papers.
Given a software paper and software, the question of which should be cited and when is
complicated, and there is no simple answer.  
As discussed in the Importance principle (\ref{principle:importance}), \textit{the software
itself should also be cited if it is directly used and was important to the work}.
If a software paper exists and it contains results (performance, validation, etc.) that are
important to the work, then the software paper should also be cited.
In addition, if the software authors ask that a paper should be cited, that should be respected.
Note that there are situations where it's appropriate to cite the software, the software paper, or both.
